### 2014-10-30 fundamentals/conclusion.tex
fixes arclong to acrlong
updated minor edits

The object-oriented \arclong{ABM} simulation paradigm ensures more generic 
simulation capability. It allows \Cyclus to address common analyses in a more 
flexible fashion and enables analyses that are impossible with system dynamics 
codes.

Similarly, discrete, fidelity-agnostic object tracking facilitates simulations 
at every level of detail. Simulations relying on arbitrarily complex isotopic 
compositions are possible in \Cyclus, as are  toy simulations not employing any 
physics at all. Indeed, agents of such varying fidelity can even exist in the 
same simulation. Researchers no longer need to reinvent the wheel in order to 
model a simulation focused on the aspects of the fuel cycle that their research 
focuses on.

>>>>

The object-oriented \acrlong{ABM} simulation paradigm ensures more generic 
simulation capability. It allows \Cyclus to address common analyses in a more 
flexible fashion and enables analyses that are impossible with system dynamics 
codes.

Similarly, discrete, fidelity-agnostic object tracking facilitates simulations 
at every level of detail. Simulations relying on arbitrarily complex isotopic 
compositions are possible in \Cyclus, as are simulations not employing any 
physics at all. Indeed, agents of such varying fidelity can even exist in the 
same simulation. Researchers no longer need to reinvent the wheel in order to 
model a simulation focused on the aspects of the fuel cycle that their research 
focuses on.

### 2014-10-30 fundamentals/examples.tex
updated minor edits

The early success of the \Cyclus simulator can be measured in many ways. 
The most compelling are demonstrations of the feasibility of the \Cyclus community-driven development 
model and of fundamental simulation capability. Nascent, promising growth of the \Cyclus 
ecosystem at multiple institutions indicates that a fuel cycle simulator can 
advance in a community-drive development paradigm. Additionally, simple 
simulations as well as more complex recycling simulations demonstrate that 
\Cyclus posesses fundamental fuel cycle simulation capabilities.

@@

The \Cyclus `Ecosystem' is the collection of tools, calculation libraries, 
archetypes, data, and input files intended for use with the \Cyclus simulator. 
Members of the ecosystem include:
\begin{itemize}
\item the archetypes provided in the \Cycamore \cite{carlsen_cycamore_2014} 
repository of additional modules,
\item the archetypes created by user-developers,
\item isotopic composition data,
\item historical facility deployment data,
\item the \Cyclus \gls{GUI} tools, Cycic and Cyclist,
\item the tools in the \Cyclus toolkit
\item and other tools for \Cyclus optimization, parallelization, and development.
\end{itemize}
All together, these form an `ecosystem' of capabilities. Over time, this 
ecosystem will grow as archetype-developers, kernel-developers, and 
even users contribute capabilities developed for their own needs. Indeed, the 
long-term vision for the \Cyclus framework predicts an ever-expanding ecosystem 
of both general and specialized capability extensions within that ecosytem.

@@

Results of some simple recycle scenarios run in \Cyclus follow.  In \Cyclus,
because material is tracked as discrete objects, single-pass MOX recycle is
easy to implement.  The simulation initially included one provider of fresh
UOX fuel, one recycled fuel fabrication facility, one reactor, one separations
facility, and one repository. The simulation duration was set to 1100 months.

@@

The \Class{Source} and \Class{Sink} modules from \Cycamore were also used as a
source of fresh, enriched uranium and a repository respectively. A simple
custom recycled fuel fabrication facility was used.  This fabrication facility
mixes fissile and fertile streams to match target fuel compositions as closely
as possible.  The method used for this matching is approximately the same as
that used by the Cosi fuel cycle simulator \TODO{cite COSI equivalence
method}. The material flows for this simulation are shown below in figure
\ref{fig:flowmodopen}.

>>>>

The success of the \Cyclus simulator can be measured in many ways. 
The most compelling are demonstrations of the feasibility of the \Cyclus community-driven development 
model and of fundamental simulation capability. Nascent promising growth of the \Cyclus 
ecosystem at multiple institutions indicates that a fuel cycle simulator can 
advance in a community-drive development paradigm. Additionally, simple 
simulations as well as more complex recycling simulations demonstrate that 
\Cyclus posesses fundamental fuel cycle simulation capabilities.

@@

The \Cyclus `Ecosystem' is the collection of tools, calculation libraries, 
archetypes, data, and input files intended for use with the \Cyclus simulator. 
Members of the ecosystem include:
\begin{itemize}
\item the archetypes provided in the \Cycamore \cite{carlsen_cycamore_2014} 
repository of additional modules,
\item the archetypes created by researchers,
\item isotopic composition data,
\item historical facility deployment data,
\item the \Cyclus \gls{GUI} tool Cyclist,
\item the tools in the \Cyclus toolkit
\item and other tools for \Cyclus optimization, parallelization, and development.
\end{itemize}
All together, these form an `ecosystem' of capabilities. Over time, this 
ecosystem will grow as archetype-developers, kernel-developers, and 
even users contribute capabilities developed for their own needs. Indeed, the 
long-term vision for the \Cyclus framework predicts an ever-expanding ecosystem 
of both general and specialized capability extensions within that ecosytem.

@@

Results of some simple recycle scenarios run in \Cyclus follow.  In \Cyclus,
because material is tracked as discrete objects, single-pass mixed-oxide (MOX) 
recycle is
easy to implement.  The simulation initially included one provider of fresh
uranium oxide (UOX) fuel, one recycled fuel fabrication facility, one reactor, one separations
facility, and one repository. The simulation duration was set to 1100 months.

@@

The \Class{Source} and \Class{Sink} archetypes from \Cycamore were also used as a
source of fresh, enriched uranium and a repository respectively. A simple
custom recycled fuel fabrication facility was used.  This fabrication facility
mixes fissile and fertile streams to match target fuel compositions as closely
as possible.  The method used for this matching is approximately the same as
that used by the Cosi fuel cycle simulator \TODO{cite COSI equivalence
method}. The material flows for this simulation are shown below in figure
\ref{fig:flowmodopen}.

### 2014-10-30 fundamentals/impl.tex
updated minor edits

A modular, agent-based is an ideal approach for solving complex, coupled,
physics-dependent supply chain problems involving material routing, facility
deployment, regional and institutional hierarchies. Additionally, the choice to 
build \Cyclus on open source libraries in modern programming languages enables 
both remote and mutiprocess execution on a number of platforms.

@@

Dynamically-loadable libraries are the primary mechanism for extending \Cyclus' capability. 
This approach provides encapsulation: the core of the code operates
completely independently from the individual plugin libraries. Thus, any
customization or extension is implemented only in the loadable
library.

This approach encourages efficient, targeted contribution to the ecosystem of 
archetype libraries.  The 
scientist-developer can focus on generating an archetype model within their
sphere of expertise, while relying on the contributions of others to fill 
in the other technologies in the simulation.  This strategy also allows individual developers to
explore different levels of complexity within their archetypes, including
wrapping other simulation tools as loadable libraries within the \Cyclus
framework.

@@

Interchangability is accomplished by providing \glspl{API} that define agent-to-agent
interaction and agent-to-environment interaction, primarily through the
\Class{Agent} and \Class{Trader} interfaces. Figure \ref{fig:agent_uml} shows 
the ``inheritance'' structure of the \Class{Agent} class in a \gls{UML} diagram 
format. It shows how the \Class{Agent} interface
provides a notion of parent-child hierarchichal relationship, where parents can
choose to \textit{build} child agents and \textit{decommission} child
agents. For the archetype developer, this interface provides enormous power, 
very simply. The \gls{API} exposes \Class{Agent} helpful functionality for 
interacting with the \Cyclus simulation kernel while abstracting away unnecessary 
detail.

@@

In a similar fasion, the \Class{Trader} interface allows agent-agent interaction through the
trading of \Class{Resource}s. Usabe archetypes in a \Cyclus simulation must
implement the \Class{Agent} interface and may optionally implement the
\Class{Trader} interface. For example, a \Class{Region} implements only the
\Class{Agent} interface, whereas a \Class{Facility} implements both the
\Class{Agent} and \Class{Trader} interface, allowing any \Class{Facility} to
trade with another \Class{Facility}.

@@

\Cyclus provides a novel representation of entities in the nuclear fuel cycle 
which mimics the reality in international nuclear power production
including facilities, institutions managing those facilities, and regions. While
some simulators (\TODO{cite DESAE}) have provided a notion of static regional
effects, \Cyclus allows for both regions and institutions to be first-class
actors in simulated fuel cycles.

@@

Two primary consequences arise from this structure. First, institutions are
responsible for building and decommissioning facilities. Accordingly, advanced
logic regarding building and decommissioning can be obtained by subclassing the
\Class{Institution} interface. Second, the \Class{Facility} class implmenets the
\Class{Trader} interface, and thus institutions and regions, respectively, can
adjust the resource flow preferences of their managed facilities. Importantly,
this novel capability allows for the modeling of preferential regional trading
of resources (e.g., tariffs) as well as preferential institutional trading
(e.g., long-term contracts).

Although concept of the \gls{RIF} hierarchy is provided, the \Cyclus kernel is
really designed to handle hierarchies of arbitrary depth.  It is just as easy
to run a simulation without regions and institutions (i.e.  only facilities)
or a simulation having archetypes that are the parents' of regions.  By
convention, institutions are mainly responsible for facility deployment, but
any archetype can have access to \Cyclus' agent deployment mechanism.  It easy
to implement agents that deploy copies of themselves, or that schedule their
own decommissioning.  Because regions, institutions, and facilities are all
just agents, they can all be implemented to exercise the full set of features
offered by the \Cyclus kernel.

@@

In \Cyclus, agents can transfer discrete resource objects between each other.
Cyclus supports two types of resources:

@@

  \item Materials: These represent typical nuclear materials with
      nuclide-based compositions.

@@

All operations performed on every resource object (splitting, combining,
decay, etc.) are tracked in detail.  This information includes the creating
agent for when resources are newly created and introduced into the simulation.
The parentage of each resource is also tracked. This makes it possible to
follow the travel history of discrete resource objects as they are transferred
between agents and powerfully impacts the ability to model 
non-proliferation-related simulation goals.

The \Cyclus kernel has built-in experimental support for decay calculations.
Materials ``remember'' the time since their last decay and agents are free to
invoke the decay function on them as desired to decay them to the current
simulation time. \Cyclus can currently operate in 2 decay modes with 2 other
modes likely to be added in future releases:

@@

    \item "never" (currently implemented) globally turns off all decay.
        Materials' decay function does nothing.

@@

In order to avoid excess decay calculations, when a material's decay function
is invoked, the material checks to see if it contains any nuclides with decay
constants that are significant with respect to the time delta for the current
decay operation.  If all the decay constants are not significant, no decay
calculation is performed and the material remains unchanged.  This error does
not accumulate because the next time the material's decay function is invoked,
the time delta will be larger. \TODO{want more detail on this decay shortcut?}
\TODO{describe decay algorithm and how it might be improved}.

@@

In large simulations there may be many material objects changing frequently, on 
the day or month timescale.
Material decay can also contribute significantly to such changes.  In order to
help avoid unnecessary runtime performance and database space impacts,
compositions in \Cyclus have some special features.  Compositions in \Cyclus are
immutable.  This immutability allows multiple material objects to all hold
references to the same composition object safely.  When operations are
performed on a material that don't change the composition, any new resulting
materials hold a reference to the same, originating composition object.
Although the decay operation generates a new, separate composition (preserving
immutability), a reference to the new composition is placed in a cache shared
by the new an originating compositions. The next time the originating
composition is decayed, this cache will be checked for a prior calculation
with the same cumulative decay time.  If one exists, the cached composition is
used.  This cache is shared by all compositions that transitively come from
the same origin.  Composition immutability in concert with decay history
caching help eliminate many redundant decay calculations in addition to
reducing the total number of composition objects.  Since each composition
object is only recorded in the database once, significant space savings also
occurs. \TODO{do we want a diagram helping show this composition caching?}

@@

In addition to the core functionality of the \Cyclus kernel, which is focused on
the minimal set of capabilities needed to implement an agent-based simulation
with dynamic resource exchange, a toolkit is provided that assists developers
and users with related simulation and nuclear engineering tasks. The toolkit is
an activly developed module module of \Cyclus, with a primary forward-looking
focus on supporting interesting \textit{in situ} (i.e., in simulation) and
\textit{ex situ} (i.e., post-processing) metric analysis tools.

@@

A series of utility classes are provided to support demand-constrained agent
(e.g. facility) deployment. Symbolic function representations of linear,
expontential, and piecewise functions are supported via the
\Class{SymbFunctionFactory} class. Such functions are used with other toolkit
classes to determine commodity demand (e.g., power demand) from user input. Four
mixin classes provide the basis for in-simulation deployment determination:
\Class{CommodityProducer}, \Class{CommodityProducerManager}, \Class{Builder},
\Class{BuildingManager}. The \Class{CommodityProducer} class provides an
interface for querying the \textit{prototypes} which have some nameplate
capacity to produce a given commdity, and the \Class{CommodityProducerManager}
provides an interface for registering \Class{CommodityProducer}s and querying
the current capacity (supply) of a commodity. The \Class{Builder} class provides
an interface for querying which prototypes can be built and interacts with the
\Class{BuildingManager}, which orders prototypes to be built. The
\Class{BuildingManager} uses a simple minimum cost algorithm to determine how
many of each prototype, $y_i$, to build given a demand, $\Phi$, capacities,
$\phi_i$, and costs $c_i$.

@@

The \Cyclus toolkit provides two useful modules for querying \Class{Material}
objects regarding physical parameters. First the \Class{MatQuery} module
provides a basic querying \gls{API}, including the atom and mass fractions of
nuclides, the number of moles of a nuclide in a material, and also the amount of
aggregate nuclides, i.e., a \Class{Composition}, in a material. The
\Class{enrichment} module provides an \gls{API} for determining enrichment-related
parameters of a material, including the separative work units (SWU) and natural
uranium required to enrich a material given provided feed, product, and tails
assays.

@@

\Cycamore \cite{carlsen_cycamore_2014}, the \Cyclus additional modules 
repository, provides a fundamental set of agent archetypes for basic simulation 
functionality within \Cyclus.  Since the \Cyclus framework relies on external 
archetypes to represent the agents within a simulation, \Cycamore provides the 
basic archetypes a new user needs to get started running simple simulations.  
These archetypes support a minimal set of fuel cycle simulation goals and 
provide, by example, a guide to new developers who would seek to contribute 
their own archetypes outside of \Cycamore.

As of version 1.0, \Cycamore contains four facility archetypes, one region 
archetype, and two institution archetypes. Short descriptions of those 
functions can be found in Table \ref{tab:cycamore}.

\begin{table}[h]
\centering
\begin{tabularx}{\textwidth}{|r|l|X|}
\hline
\textbf{Agent Type} & \textbf{Archetype} & \textbf{Functionality} \\
\hline
Facility & BatchReactor & A reactor model that handles batch refuelling, based on pre-determined recipes of compositions. \\
Facility & Source & This facility generates material of the composition and commodity type specified as input.  \\
Facility & Sink & This facility is capable of accepting a finite or infinite quantity of some commodity produced in the simulation \\
Facility & EnrichmentFacility & This facility enriches uranium at a specified capacity. \\
Institution& ManagerInst & The manager institution manages production of commodiites among its facilities by building new necessary ones \\
Institution & DeployInst &  This institution deploys specific facilities as defined explicitly in the input file. \\
Region & GrowthRegion & This region determines whether there is a need to meet a certain capacity (as defined via input) at each time step \\
\hline
\end{tabularx}
\caption{The Archetypes in \Cycamore seek to cover a large range of simple simulation use cases.}
\label{tab:cycamore}
\end{table}

>>>>

A modular, agent-based approach is ideal for solving complex, coupled,
physics-dependent supply chain problems involving material routing, facility
deployment, regional and institutional hierarchies. Additionally, the choice to 
build \Cyclus on open source libraries in modern programming languages enables 
both remote and mutiprocess execution on a number of platforms.

@@

Dynamically-loadable libraries are the primary mechanism for extending \Cyclus' capability. 
This approach provides encapsulation. The core of the code operates
completely independently from the individual plugin libraries. Thus, any
customization or extension is implemented only in the loadable
library.

This approach encourages efficient, targeted contribution to the ecosystem of 
archetype libraries.  The 
researchercan focus on generating an archetype model within their
sphere of expertise, while relying on the contributions of others to fill 
in the other technologies in the simulation.  This strategy also allows individual developers to
explore different levels of complexity within their archetypes, including
wrapping other simulation tools as loadable libraries within the \Cyclus
framework.

@@

Interchangability is accomplished by providing \glspl{API} that define agent-to-agent
interaction and agent-to-environment interaction, primarily through the
\Class{Agent} and \Class{Trader} interfaces. Figure \ref{fig:agent_uml} shows 
the ``inheritance'' structure of the \Class{Agent} class in a \gls{UML} diagram 
format. It shows how the \Class{Agent} interface
provides a notion of parent-child hierarchichal relationship, where parents can
choose to \textit{deploy} child agents and \textit{decommission} child
agents. For the archetype developer, this interface provides enormous power, 
very simply. The \gls{API} exposes \Class{Agent} helpful functionality for 
interacting with the \Cyclus simulation kernel while abstracting away unnecessary 
detail.

@@

In a similar fasion, the \Class{Trader} interface allows agent-agent interaction through the
trading of \Class{Resource}s. Archetypes in a \Cyclus simulation must
implement the \Class{Agent} interface and may optionally implement the
\Class{Trader} interface. For example, a \Class{Region} implements only the
\Class{Agent} interface, whereas a \Class{Facility} implements both the
\Class{Agent} and \Class{Trader} interface, allowing any \Class{Facility} to
trade with another \Class{Facility}.

@@

\Cyclus provides a novel representation of entities in the nuclear fuel cycle 
which models the reality in international nuclear power production
encompassing facilities, institutions managing those facilities, and regions. While
some simulators (\TODO{cite DESAE}) have provided a notion of static regional
effects, \Cyclus allows for both regions and institutions to be first-class
actors in simulated fuel cycles.

@@

Two primary consequences arise from this structure. First, institutions are
nominally
responsible for deploying and decommissioning facilities. Accordingly, advanced
logic regarding building and decommissioning can be obtained by subclassing the
\Class{Institution} interface. Second, the \Class{Facility} class implmenets the
\Class{Trader} interface, and thus institutions and regions, respectively, can
adjust the resource flow preferences of their managed facilities. Importantly,
this capability allows for the modeling of preferential regional trading
of resources (e.g., tariffs) as well as preferential institutional trading
(e.g., long-term contracts).

Although concept of the \gls{RIF} hierarchy is provided, the \Cyclus kernel is
designed to handle hierarchies of arbitrary depth.  It is capable of 
running a simulation without regions and institutions (i.e.  only facilities)
or a simulation having archetypes that are the parents of regions.  By
convention, institutions are mainly responsible for facility deployment, but
any archetype can have access to the \Cyclus agent deployment mechanism.  It easy
to implement agents that deploy copies of themselves, or that schedule their
own decommissioning.  Because regions, institutions, and facilities are all
agents, they can all be implemented to exercise the full set of features
offered by the \Cyclus kernel.

@@

In \Cyclus, agents can transfer discrete resource objects between each other.
Cyclus currently supports two types of resources:

@@

  \item Materials: These represent typical nuclear materials with
      nuclide compositions.

@@

All operations performed on every resource object (splitting, combining,
decay, etc.) are tracked in detail as they are performed.  This information includes 
the creating
agent for when resources are newly created and introduced into the simulation.
The parentage of each resource is also tracked. This makes it possible to
follow the history of resources as they are transferred
between agents.  This powerfully impacts the ability to model 
non-proliferation-related simulation goals.

The \Cyclus kernel has built-in experimental support for decay calculations.
Materials store the time since their last decay and agents are free to
invoke the decay function on them as desired to decay them to the current
simulation time. \Cyclus can currently operate in 2 decay modes with 2 other
modes likely to be added in future releases:

@@

    \item "never" (currently implemented) globally turns off all decay.
        Materials decay function does nothing.

@@

In order to avoid excess decay calculations, when decay 
is invoked, the material checks to see if it contains any nuclides with decay
constants that are significant with respect to the time delta for the current
decay operation.  If all the decay constants are not significant, no decay
calculation is performed and the material remains unchanged.  This error does
not accumulate because the next time the material's decay function is invoked,
the time delta will be larger. \TODO{want more detail on this decay shortcut?}
\TODO{describe decay algorithm and how it might be improved}.

@@

In large simulations there may be many material objects changing frequently.
Material decay can also contribute significantly to such changes.  In order to
help avoid unnecessary runtime performance and database space impacts,
compositions in \Cyclus have some special features.  Compositions in \Cyclus are
immutable.  This immutability allows multiple material objects to all hold
references to the same composition object safely.  When operations are
performed on a material that do not change the composition, any new resulting
materials hold a reference to the same, originating composition object.
Although the decay operation generates a new, separate composition (preserving
immutability), a reference to the new composition is placed in a cache shared
by the new originating compositions. The next time the originating
composition is decayed, the cache will be checked for a prior calculation
with the same cumulative decay time.  If one exists, the cached composition is
used.  This cache is shared by all compositions that transitively come from
the same origin.  Composition immutability in concert with decay history
caching help eliminate many redundant decay calculations in addition to
reducing the total number of composition objects.  Since each composition
object is only recorded in the database once, significant space savings also
occurs. \TODO{do we want a diagram helping show this composition caching?}

@@

In addition to the core functionality of the \Cyclus kernel, which is focused on
the set of capabilities needed to implement an agent-based simulation
with dynamic resource exchange, a toolkit is provided that assists developers
and users with related simulation and nuclear engineering tasks. The toolkit is
an activly developed part of \Cyclus, with a primarily forward-looking
focus on supporting interesting \textit{in situ} metric analysis tools.

@@

A series of utility classes are provided to support demand-constrained agent
facility deployment. Symbolic function representations of linear,
expontential, and piecewise functions are supported via the
\Class{SymbFunctionFactory} class. Such functions are used with other toolkit
classes to determine commodity demand (e.g., power demand) from user input. Four
mixin classes provide the basis for in-simulation deployment determination:
\Class{CommodityProducer}, \Class{CommodityProducerManager}, \Class{Builder},
\Class{BuildingManager}. The \Class{CommodityProducer} class provides an
interface for querying the \textit{prototypes} which have the
capacity to produce a given commdity. The \Class{CommodityProducerManager}
provides an interface for registering \Class{CommodityProducer}s and querying
the current capacity (supply) of a commodity. The \Class{Builder} class provides
an interface for querying which prototypes can be built and interacts with the
\Class{BuildingManager}, which orders prototypes to be built. The
\Class{BuildingManager} uses a simple minimum cost algorithm to determine how
many of each prototype, $y_i$, to build given a demand, $\Phi$, capacities,
$\phi_i$, and costs $c_i$.

@@

The \Cyclus toolkit provides two useful interfaces for querying \Class{Material}
objects regarding physical parameters. First the \Class{MatQuery} module
provides a basic querying \gls{API}, including the atom and mass fractions of
nuclides, the number of moles of a nuclide in a material, and also the amount of
aggregate nuclides, i.e., a \Class{Composition}, in a material. The
\Class{enrichment} module provides an \gls{API} for determining enrichment-related
parameters of a material, including the separative work units (SWU) and natural
uranium required to enrich a material given provided feed, product, and tails
assays.

@@

\Cycamore \cite{carlsen_cycamore_2014}, the \Cyclus additional module
repository, provides a fundamental set of agent archetypes for basic simulation 
functionality within \Cyclus.  Since the \Cyclus framework relies on external 
archetypes to represent the agents within a simulation, \Cycamore provides the 
basic archetypes a new user needs to get started running simple simulations.  
These archetypes support a minimal set of fuel cycle simulation goals and 
provide, by example, a guide to new developers who would seek to contribute 
their own archetypes outside of \Cycamore.

As of version 1.0, \Cycamore contains four facility archetypes, one region 
archetype, and two institution archetypes. Short descriptions of these 
functions can be found in Table \ref{tab:cycamore}.

\begin{table}[h]
\centering
\begin{tabularx}{\textwidth}{|r|l|X|}
\hline
\textbf{Entity} & \textbf{Archetype} & \textbf{Functionality} \\
\hline
Facility & BatchReactor & A reactor model that handles batch refuelling, based on pre-determined recipes of compositions. \\
Facility & Source & This facility generates material of the composition and commodity type specified as input.  \\
Facility & Sink & This facility is capable of accepting a finite or infinite quantity of some commodity produced in the simulation \\
Facility & EnrichmentFacility & This facility enriches uranium at a specified capacity. \\
Institution& ManagerInst & The manager institution manages production of commodiites among its facilities by building new necessary ones \\
Institution & DeployInst &  This institution deploys specific facilities as defined explicitly in the input file. \\
Region & GrowthRegion & This region determines whether there is a need to meet a certain capacity (as defined via input) at each time step \\
\hline
\end{tabularx}
\caption{The Archetypes in \Cycamore seek to cover a large range of simple simulation use cases.}
\label{tab:cycamore}
\end{table}
